A Study of Common Bug Fix Patterns in Rust

### 2022-11-25 results.tex
little change

We collected random samples 1000 times. In each iteration, 50 datapoints are sampled from our general and borrow-checker databases (25 each). For each database, out of the 1000 sample sets, we picked the one that minimized the sampling error. The sampling error is defined as the average of the absolute differences between the sample set mean and the total mean per column~\citep{degroot2012probability}. Also, these random samples are drawn from the clustered datapoints. The reason behind this decision is the same as why we collected a lot of noise points, that is, the majority of the commits involve changes in many program elements and the key changing elements are difficult to determine.

We carried out a manual experiment for evaluating our code embedding. In the experiment, the human analyzer looks at the change's source code and finds the most important element that appears in the circle pack figure, recording its rank. A value of 1 indicates that the human analyzer concurs with the algorithm, while 2 means that the human-identified most important element was ranked 2 by the algorithm. After collecting all the ranks, then we calculate Top-$n$ Accuracy for $n=1$ up to $n=5$. Both authors acted as analyzer and carried out the experiment independently. We report the results as the fraction of the changes on which both authors agreed upon its embedding correctness. The final results are shown in Figure~\ref{fig:rq1}.

>>>>

We collected random samples 1000 times. In each iteration, we sampled 50 datapoints from our general and borrow-checker databases (25 each). For each database, out of the 1000 sample sets, we picked the one that minimized the sampling error. The sampling error is defined as the average of the absolute differences between the sample set mean and the total mean per column~\citep{degroot2012probability}. Also, these random samples are drawn from the clustered datapoints. The reason behind this decision is the same as why we collected a lot of noise points, that is, the majority of the commits involve changes in many program elements and the key changing elements are difficult to determine.

We carried out a manual experiment for evaluating our code embedding. In the experiment, the human analyzer looks at the change's source code and finds the most important element that appears in the circle pack figure, recording its rank. A value of 1 indicates that the human analyzer concurs with the algorithm, while 2 means that the human-identified most important element was ranked 2 by the algorithm. After collecting all the ranks, then we calculate Top-$n$ Accuracy for $n=1$ up to $n=5$. Both authors acted as analyzer and carried out the experiment independently. To avoid inflating our final results, after comparing the ranks that the authors gave to each datapoint, we consider the larger (worse) rank in our final results. That is, if the first author gave rank 2 to datapoint $D$ and the second author gave rank 3 to that datapoint, in the final results we gave datapoint $D$ a rank of 3. The final results are shown in Figure~\ref{fig:rq1}.
